Algorithm explanation

### 2013-04-30 article/algo.tex
Changes in expression

\begin{align*}
\mathcal{HC}_v & = \left( \bigwedge_{(u,v,\theta) \in E} \theta \varphi(u) \right) \Longrightarrow \varphi(succ(v)) \\
\llbracket G \rrbracket & = \bigwedge_{v \in V} \mathcal{HC}_v
\end{align*}

We implicitly assume each $\mathcal{HC}_v$ is universally quantified
by its all free variables $FV(\mathcal{HC}_v)$.

@@

Given an acyclic Horn graph (or called a Horn DAG), we define the
relation $u <^+ v$ over $V_T$ as follows.
\[ u <^+ v \Longleftrightarrow \exists a, \theta; \left\lbrace{ (u,a,\theta), (a,v,\emptyset) \right\rbrace \subseteq E \]
By the assumption that $G$ is acyclic, $<^+$ is a well-founded
relation. We assume without loss of generality that $V_T$ contains the
greatest element $v_\bot$ with respect to $<^+$; otherwise we can
always implicitly assume $\varphi(v_\bot) = 0 \leq 0$ such that $\forall v \in V_\bot; \exists v_a; \left\lbrace (v, v_a, \emptyset), (v_a, v_\bot, \emptyset) \right\rbrace \subseteq E $.

For each $v \in V_T$, we define
$\Delta(v) = (\mathbf{a}_v \mathbf{x} \leq b_v, C_v)$
, where
\begin{itemize}
\item $\mathbf{a}_v \mathbf{x} \leq b_v$ is a linear inequality that
  may contain coefficient variables
\item $C_v$ is a set of linear expressions on coefficient variables.
\end{itemize}
Intuitively, the pair $(\mathbf{a} \mathbf{x} \leq b, C)$ denotes the
set of inequalities:

\begin{align*}
\left\lbrace
 \mathbf{a} \mathbf{x} \leq b \middle|
 \exists \left( FV(C)
  \setminus (\mathbf{a} \cup \left\lbrace b \right\rbrace
 \right); C
\right\rbrace
\end{align*}

$\Delta(v)$ is defined by well-founded induction on $v$ with respect
to the relation $<^+$. Then,
$\Delta(v) = \left( \mathbf{a}_v \mathbf{x} \leq b_v, C_v \right)$,
where

\begin{align*}
C_v = & \bigcup_{u <^+ v} C_u
\\
& \cup \begin{cases}
\emptyset
& \mbox{if } \nexists u; u <^+ v \\
\left\lbrace
 \mathbf{a}_v = \sum_{u <^+ v} \mathbf{a}_u,
 b_v \geq \sum_{u <^+ v} b_u
\right\rbrace
& \mbox{otherwise}
\end{cases}
\\
& \cup \begin{cases}
\emptyset
& \mbox{if } \varphi(v) = P(\mathbf{x}) \\
\left\lbrace
 \lambda_v \geq 0, \mathbf{a}_v = \lambda_v \mathbf{a}_0,
 b_v = \lambda_v b_0
\right\rbrace
& \mbox{if } \varphi(v) = \mathbf{a}_0 \mathbf{x} \leq b_0
\end{cases}
\end{align*}

>>>>

\begin{align*}
\mathcal{HC}_v & = \left( \bigwedge_{(u,v,\theta) \in E} \theta \varphi(u) \right) \Longrightarrow \varphi(succ(v)) \\
\llbracket G \rrbracket & = \bigwedge_{v \in V_\Rightarrow} \mathcal{HC}_v
\end{align*}

We implicitly assume each $\mathcal{HC}_v$ is universally quantified
by its all free variables $\textsc{FV}(\mathcal{HC}_v)$.

@@

Given an acyclic Horn graph (or called a Horn DAG), we define the
relation $u <^+ v$ over $V_T$ as follows.
\[ u <^+ v \Longleftrightarrow \exists a, \theta; \left\lbrace (u,a,\theta), (a,v,\emptyset) \right\rbrace \subseteq E \]
By the assumption that $G$ is acyclic, $<^+$ is a well-founded
relation. We assume without loss of generality that $V_T$ contains the
greatest element $v_\bot$ with respect to $<^+$; otherwise we can
always implicitly assume $\varphi(v_\bot) = 0 \leq 0$ such that $\forall v \in V_\bot; \exists v_a; \left\lbrace (v, v_a, \emptyset), (v_a, v_\bot, \emptyset) \right\rbrace \subseteq E $.

For each $v \in V_T$, we define
$\Delta(v) = (\mathbf{a}_v \mathbf{x}_v \leq b_v, C_v)$
, where
\begin{itemize}
\item $\mathbf{a}_v \mathbf{x}_v \leq b_v$ is a linear inequality that
  contains coefficient variables $\mathbf{a}_v$, and
\item $C_v$ is a set of linear expressions on coefficient variables.
\end{itemize}
Intuitively, the pair $(\mathbf{a} \mathbf{x} \leq b, C)$ denotes the
set of inequalities:

\begin{align*}
\left\lbrace
 \mathbf{a} \mathbf{x} \leq b \middle|
 \exists \left( \textsc{FV}(C)
  \setminus (\mathbf{a} \cup \left\lbrace b \right\rbrace
 \right); C
\right\rbrace
\end{align*}

$\Delta(v)$ is defined by well-founded induction on $v$ with respect
to the relation $<^+$. Then, $C_v$ in
$\Delta(v) = \left( \mathbf{a}_v \mathbf{x}_v \leq b_v, C_v \right)$
can be shown as follows.

\begin{align*}
C_v = & \bigcup_{u <^+ v} C_u
\\
& \cup \begin{cases}
\emptyset
& \mbox{if } \nexists u; u <^+ v \\
\left\lbrace
 \mathbf{a}_v \mathbf{x}_v = \sum_{u <^+ v} \mathbf{a}_u \theta_{u,v} (\mathbf{x}_u),
 b_v \geq \sum_{u <^+ v} b_u
\right\rbrace
& \mbox{otherwise}
\end{cases}
\\
& \cup \begin{cases}
\emptyset
& \mbox{if } \varphi(v) = P(\mathbf{x}) \\
\left\lbrace
 \lambda_v \geq 0, \mathbf{a}_v = \lambda_v \mathbf{a}_0,
 b_v = \lambda_v b_0
\right\rbrace
& \mbox{if } \varphi(v) = \mathbf{a}_0 \mathbf{x} \leq b_0
\end{cases}
\end{align*}

For simplicity, we assume variables $\mathbf{a}_u$, $\mathbf{x}_u$,
$b_u$ are obtained from $\Delta(u)$ in each $\sum_{u <^+ v}$. Also, a
renaming function $\theta_{u,v}$ is shorthand for $\theta$ such that
$\exists a; \left\lbrace (u,a,\theta), (a,v,\emptyset) \right\rbrace
\subseteq E$, and here we pass a variable vector to it.
